% !TeX root = ./main.tex
% !TeX spellcheck = en_US
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS **START**
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
    \topmargin=-0.5in
    \oddsidemargin -.5in
    \evensidemargin -.5in
    \textwidth=6.5in
    \itemsep=0in
    \parsep=0in
    \newsectionwidth{1in}
    \usepackage[pdftex]{graphicx}
    \usepackage{enumitem}
    \usepackage{wrapfig}
    \usepackage{helvet}
    \usepackage{fancyhdr}
    \renewcommand{\headrulewidth}{0mm}
    \usepackage[colorlinks = true,
                linkcolor = blue,
                urlcolor  = blue,
                citecolor = blue,
                anchorcolor = blue]{hyperref}
    \setlength{\textwidth}{6.5in} % Text width of the document
    \setlength{\textheight}{720pt}
    \pagestyle{fancy}
    \fancyhf{}
    \fancyfoot[R]{\small{\href{https://resume.sangam.dev}{resume.sangam.dev}}}
    %----------------------------------------------------------------------------------------
    %	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS **END**
    %----------------------------------------------------------------------------------------
\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION **START**
%----------------------------------------------------------------------------------------
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{\href{https://www.sangam.dev}{SANGAM KUMAR}}
\end{center}
\vspace{-7mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.3pt}
\vspace{-9mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:meetsangamcse@gmail.com}{meetsangamcse@gmail.com} ~\textbullet~ \(+91\)
    7602054727 ~\textbullet~ Bangalore, Karnataka, India
\end{center}
\vspace{-7mm}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION **END**
%----------------------------------------------------------------------------------------
\begin{resume}
    %----------------------------------------------------------------------------------------
    %	EDUCATION SECTION **START**
    %----------------------------------------------------------------------------------------
    \section{Education}
    \textbf{B.Tech in CSE} -
    \href{https://www.nitsikkim.ac.in/}{National Institute of Technology Sikkim} \hfill 2015 - 2019 \\
    % \begin{itemize}
    %     \item CGPA of \textbf{7.40}/10 (Dec 2018)
    % \end{itemize}
    \textbf{High School} - Hare Krishna H/S Vidyalay, Vaishali, Bihar (BSEB) \hfill 2015 \\
    \textbf{Secondary School} - Krishnanand Memorial Academy, Munger, Bihar (CBSE) \hfill 2012
    %----------------------------------------------------------------------------------------
    %	EDUCATION SECTION **END**
    %----------------------------------------------------------------------------------------

    %----------------------------------------------------------------------------------------
    %	EXPERIENCE SECTION **START**
    %----------------------------------------------------------------------------------------
    \section{Experience}
    \textbf{Software Development Engineer at \href{https://www.hackerrank.com}{HackerRank, Bangalore}} \hfill June, 2019 - Present \\
    Developing Enterprise softwares for \href{https://www.hackerrank.com/products/projects}{Projects} team. Owns/maintain code base for \href{https://www.hackerrank.com/products/projects#role5}{DevOps Engineers Accessment tool},
    built on top of AWS EC2 Instances, which is used to access candidates for DevOps Engineering role. Currently working on automated scoring for candidates.\\
    \\
    \textbf{Software Development Engineering Intern at \href{https://www.hackerrank.com}{HackerRank, Bangalore}} \\
    \emph{Mentored by \href{https://www.hackerrank.com/about-us/our-team/}{Harishankaran
            Karunanidhi}\footnotesize{, CTO \& Co-Founder}} \hfill Jan, 2019 - June, 2019 \\
    Worked closely on the payment automation using Stripe API to generate billing receipts for
    the Enterprise customers and send the bills to a given billing email. Implemented a method to check the browser's compatibility
    for \href{https://www.hackerrank.com/statuscheck}{statuscheck} page. Migrated contests' pages from
    BackboneJS code to ReactJS e.g, \href{https://www.hackerrank.com/projecteuler/}{contest projecteuler}.
    Implemented a comment box for \href{https://www.hackerrank.com/work}{HackerRank's Sourcing} platform
    which appears to the recruiters for the candidate who attempts a recruiting test. Built an UI Icon library
    using SVGR which transforms given SVGs to desired React's Component, and added Babel config to compile
    the Components. Main stacks used are RoR and ReactJS. \\
    \\
    \textbf{Winter Research Intern in \href{http://acslab.org}{Applied Cognitive Science Lab,} \href{https://iitmandi.ac.in/}{IIT Mandi}} \\
    \emph{Mentored by \href{https://faculty.iitmandi.ac.in/~varun/}{Dr. Varun Dutt, SCEE and SHSS, IIT Mandi}} \hfill Nov, 2017 - Jan, 2018 \\
    Developed a solution to fetch sensor’s data deployed under soil and save it to the database for the
    \href{http://landslidemonitoring.esy.es/}{Low Cost Early Warning Solution for Landslide} using Arduino
    and 12 geological sensors. The sensors are used to collect the data values of an amount of rainfall,
    soil moisture, and angle variations. The data collected from the sensor triplets placed in different
    locations are sent to the cloud server via GSM. Created a solution to predict landslide by using z-score
    of total collected soil movement’s data and send alert to people, using SMS-PP (Short Message Service,
    Point-to-Point) and SMS-CB (Short Message Service, Cell Broadcast) to pre-warn the people in the areas
    of increased risk of danger. \\
    \\
    \textbf{Summer Trainee, \href{http://www.mnnit.ac.in/}{Motilal Nehru National Institute of Technology}} \hfill Jun, 2017 - Jul, 2017 \\
    Attended 200 hrs of training on Enhancing Skill for Enterprise Scale Application Development and built a Registration
    Portal for workshop registrations using JSP, MySQL, and Bootstrap.

    %----------------------------------------------------------------------------------------
    %	EXPERIENCE SECTION **END**
    %----------------------------------------------------------------------------------------

    %----------------------------------------------------------------------------------------
    %	VOLUNTEER SECTION **START**
    %----------------------------------------------------------------------------------------
    \section{Volunteer}
    \textbf{Student Developer, \href{https://summerofcode.withgoogle.com/}{Google Summer of Code 2018}} \\
    \emph{Software Developer at \href{https://coala.io/}{coala.io}} \hfill Apr, 2018 - Aug, 2018 \\
    Worked on the enhancement of automated tests of \href{https://github.com/coala/coala}{coala},
    an open-source language independent code analysis tool, written in Python, and base
    class of \href{https://github.com/coala/coala-bears}{coala-bears} and its tests.
    \href{https://github.com/coala/cEPs/blob/master/cEP-0027.md}{Code Enhancement Proposal} can be found
    in \href{https://github.com/coala/cEPs}{coala/cEPs} repository. Also, created 2 bears(static analysis tools)
    for Ruby and 1 bear for Crystal by wrapping Brakeman, Fasterer and Ameba respectively. \\
    \\
    \textbf{Student Developer, \href{https://kwoc.kossiitkgp.in}{Kharagpur Winter of Code 2017}} \\
    \emph{Software Developer at \href{https://coala.io/}{coala.io}} \hfill 1 Dec, 2017 - 31 Dec, 2017 \\
    Updated html-linter from version 0.3.0 to 0.4.0 of
    \href{https://github.com/coala/coala-bears/pull/2148/commits/631ed37f7322fae7b9d7e16616f8c4009b9adb7e}{HTMLLintBear}
    and fixed \href{https://github.com/coala/coala-bears/blob/master/bears/python/PyLintBear.py}{PyLintBear} which was
    breaking on Python 3.5.0. \\
    \\
    \textbf{Web Developer, \href{https://nitsikkim.ac.in/webdevelopmentcell}{Web Development Cell (WDC), NIT Sikkim}} \hfill Jan, 2017 - May, 2019 \\
    Worked with the WDC Team to develop institute's dynamic website. The website, deployed at
    \href{https://www.nitsikkim.ac.in}{nitsikkim.ac.in}, uses PHP and MySQL as initial tools
    and Bootstrap framework for stylesheets. I lead the Image Processing Team and maintain
    \href{https://placement.nitsikkim.ac.in}{placement.nitsikkim.ac.in}.
    %----------------------------------------------------------------------------------------
    %	VOLUNTEER SECTION **END**
    %----------------------------------------------------------------------------------------

    %----------------------------------------------------------------------------------------
    %	TECHNICAL SKILLS SECTION **START**
    %----------------------------------------------------------------------------------------
    \section{Technical \hspace{2mm} Skills}
    \textbf{Strongest Areas} - Web Development, Databases, Algorithms \\
    \textbf{Languages}
    \begin{itemize}
        \item \textbf{\textsl{Proficient}} - Ruby, Python, JavaScript, C/C++, Bash, PHP
        \item \textbf{\textsl{Familiar}} - Dart, Java
    \end{itemize}
    \textbf{Tools/Frameworks}
    \begin{itemize}
        \item \textbf{\textsl{Proficient}} - ReactJS, Ruby on Rails, MySQL, Flutter, Git, AWS, GCP, Docker, Unix-System (Linux \& MacOS)
        \item \textbf{\textsl{Familiar}} - Django
    \end{itemize}
    %----------------------------------------------------------------------------------------
    %	TECHNICAL SKILLS SECTION **END**
    %----------------------------------------------------------------------------------------

    %----------------------------------------------------------------------------------------
    %	RELEVANT COURSE SECTION **START**
    %----------------------------------------------------------------------------------------
    % \section{Relevant \hspace{2mm} Courses}
    % Data Structures and Algorithms, Operating System, Computer Graphics, Computer Networks,
    % Databases, Automata Theory, Distributed Computing, Software Engineering, Computer Organisation, Deep Learning, Natural Language Processing
    %----------------------------------------------------------------------------------------
    %	RELEVANT COURSE SECTION **END**
    %----------------------------------------------------------------------------------------

    %----------------------------------------------------------------------------------------
    %	CURRENT RESEARCH SECTION **START**
    %----------------------------------------------------------------------------------------
    % \section{Recent Research}
    % Research on Firefly algorithm (a new swarm intelligence algorithm) for big data optimization.
    %----------------------------------------------------------------------------------------
    %	CURRENT RESEARCH SECTION **END**
    %----------------------------------------------------------------------------------------

    %----------------------------------------------------------------------------------------
    %	SELECTED PROJECTS SECTION **START**
    %----------------------------------------------------------------------------------------
    \section{Selected Projects}
    All projects available on git : \url{https://www.github.com/sangamcse}
    \begin{itemize}[leftmargin=*]
        \item \textbf{\href{https://github.com/sangamcse/online-examination-system}{Online Examination System}} :
              Developed a MCQ-based online examination tool using PHP, MySQL, HTML, JavaScript and Bootstrap.
        \item \textbf{\href{https://github.com/sangamcse/registration-ESAD}{Registration System for workshop}} :
              Developed a registration system along with a chat room system which has image upload and update system,
              using JSP, PHP, MySQL, HTML and Bootstrap.
        \item \textbf{\href{https://github.com/sangamcse/calculator}{Google Calculator for iOS}} : Created a Google
              Calculator like basic Calculator for iOS app using Swift.
        \item \textbf{\href{https://github.com/sangamcse/myPNRStatus}{PNR Status Checker}} : Created a CLI tool
              to check passenger name record in Indian Railway Journey, using Python3 and requests module.
        \item \textbf{\href{https://github.com/sangamcse/Snake_game}{Snake Game}} : Created a script for snake game using
              Python2 and curses module.
        \item \textbf{\href{http://abhiyantran.nitsikkim.ac.in/abhiyantran-17/}{Abhiyantran'17 Website}} : A website for technical festival of NIT Sikkim.
    \end{itemize}
    %----------------------------------------------------------------------------------------
    %	SELECTED PROJECTS SECTION **END**
    %----------------------------------------------------------------------------------------

    %----------------------------------------------------------------------------------------
    %	ACHIEVEMENT SECTION **START**
    %----------------------------------------------------------------------------------------
    \section{Achievements and Awards}
    \begin{itemize}[leftmargin=*]
        \item Former Mentor at \href{https://summerofcode.withgoogle.com/}{Google Summer of Code 2019}.
        \item Former Software Development Engineering Intern at \href{https://www.hackerrank.com}{HackerRank, Bangalore}.
        \item Former Mentor at \href{https://codein.withgoogle.com}{Google Code-in 2018}.
        \item Former Student Developer at \href{https://summerofcode.withgoogle.com/}{Google Summer of Code 2018}.
        \item Software Developer at \href{https://coala.io}{coala.io}.
        \item Former Mentor at \href{https://kwoc.kossiitkgp.org/}{Kharagpur Winter of Code 2018}.
        \item Former Student Coordinator of \href{http://placement.nitsikkim.ac.in/}{Training and Placement Cell, NIT Sikkim}.
        \item Former Image Processing Team Lead of \href{https://nitsikkim.ac.in/webdevelopmentcell}{Web Development Cell, NIT Sikkim}.
        \item Active participation on online competitive coding websites - \href{https://www.hackerrank.com/sangamcse}{HackerRank},
              \href{https://www.hackerearth.com/@damonsangam}{HackerEarth}, etc. \\
              Member Handle - sangamcse
        \item Selected for \href{https://www.hackerearth.com/university}{HackerEarth Campus Ambassador} Program.
        \item Joint Team Member of Technical Talk at Abhiyantran 2017.
        \item Creativity Team Lead of Abhiyantran 2017 - Tech fest of NIT Sikkim.
        \item Creativity Team Lead of Udgam 2017 - Cultural fest of NIT Sikkim.
    \end{itemize}
    %----------------------------------------------------------------------------------------
    %	ACHIEVEMENT SECTION **END**
    %----------------------------------------------------------------------------------------

    %----------------------------------------------------------------------------------------
    %	HOBBIES SECTION **START**
    %----------------------------------------------------------------------------------------
    \section{Hobbies}
    Contributing to Open Source, Traveling, Photography
    %----------------------------------------------------------------------------------------
    %	HOBBIES SECTION **END**
    %----------------------------------------------------------------------------------------

    \section{More}
    Please visit \href{https://www.sangam.dev}{https://www.sangam.dev}

\end{resume}
\end{document}
