% !TeX root = ./SANGAM_KUMAR.tex
% !TeX spellcheck = en_US
%______________________________________________________________________________________________________________________
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
\documentclass[margin,line]{resume}
    \topmargin=-10mm
    \oddsidemargin -.5in
    \evensidemargin -.5in
    \textwidth=6.5in
    \itemsep=0in
    \parsep=0in
    \newsectionwidth{1in}
    \textheight=250mm
    \usepackage[pdftex]{graphicx}
    \usepackage{multicol}
    \usepackage{hyperref}
    \usepackage{enumitem}
    \setlist{nosep}
    \setlength{\columnsep}{1cm}

\begin{document}
\name{\huge{Sangam Kumar}}
\begin{resume}
    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
    \href{tel:+917602054727}{+91-7602054727}                                      \hfill    \url{https://sangam.dev}\\%
    \href{mailto:meetsangamcse@gmail.com}{meetsangamcse@gmail.com}      \hfill    \url{https://github.com/sangamcse}\\%
    \null                                                            \hfill    \url{https://linkedin.com/in/sangamcse}%

    %__________________________________________________________________________________________________________________
    % Experience
    \section{\mysidestyle Experience}

    \textbf{HackerRank                                                                     \hfill    Bangalore, IN} \\%
    \emph{Software Development Engineer II                                          \hfill    Jan. 2021 -- Present} \\%
    \emph{Software Development Engineer I                                           \hfill    July. 2019 -- Jan. 2021}%
    \begin{list}{$\circ$}{}
        \item Scaled SudoRank, a DevOps Engineers Assessment tool, to 5x to support thousands of concurrent sessions of
              EC2 instances.
        \item Worked with HackerRank Projects team to deliver features that assess role-specific skills with full     %
              access to complete application environments
    \end{list}
    \emph{Software Development Engineer Intern                                      \hfill    Jan. 2019 -- July. 2019}%
    \begin{list}{$\circ$}{}
        \item Joined HackerRank Community team. Migrated components from Backbone to React.
        \item Developed an Icon library which transforms SVG icon to a React component.
        \item Improved the method to compute HackerRank's compatibility with user's browser.
    \end{list}

    \textbf{Google Summer of Code                                                                 \hfill    Remote} \\%
    \emph{Student Developer                                                         \hfill    Apr. 2018 -- Aug. 2018} %
    \begin{list}{$\circ$}{}
        \item Joined \url{https://coala.io} organisation. Proposed code enhancement for coala Bears Testing API       %
              \url{https://github.com/coala/cEPs/blob/master/cEP-0027.md}.
        \item Improved automated tests of \url{https://github.com/coala/coala}, an open-source language independent
              code analysis tool.
        \item Created 2 Bears(static analysis tools) for Ruby and 1 Bear for Crystal by wrapping Brakeman, Fasterer and
              Ameba respectively.
    \end{list}

    \textbf{IIT Mandi                                                                          \hfill    Mandi, IN} \\%
    \emph{Research Intern                                                           \hfill    Nov. 2017 -- Jan. 2018} %
    \begin{list}{$\circ$}{}
        \item Joined Applied Cognitive Science Lab. Improved prediction model of landslide data using z-score of      %
              collected data of soil movements.
    \end{list}

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{National Institute of Technology Sikkim                                           \hfill    Sikkim, IN} \\%
    \emph{Bachelor of Technology, Computer Science                                   \hfill    Aug. 2015 -- May. 2019}%

    %__________________________________________________________________________________________________________________
    % Projects
    \section{\mysidestyle Projects}
    All Public Projects are available at my GitHub profile: \url{https://github.com/sangamcse}                        %
    \vspace{-3mm}
    \begin{multicols}{2}
        \textbf{\href{https://github.com/sangamcse/theme-shadow-vscode}{VS Code Theme Shadow}}                      \\%
        \emph{ECMAScript}
        \begin{list}{$\circ$}{}
            \item A customizable VS Code editor dark theme.
        \end{list}

        \textbf{\href{https://github.com/sangamcse/myPNRStatus}{Train Ticket Status CLI}}                           \\%
        \emph{Python}
        \begin{list}{$\circ$}{}
            \item A CLI tool to check passenger name record in Indian Railway, using Python3 and requests module.     %
        \end{list}

        \textbf{\href{https://github.com/sangamcse/abhiyantran-2017}{Abhiyantran, 2017}}                            \\%
        \emph{JavaScript, JQuery, Php}
        \begin{list}{$\circ$}{}
            \item An interactive college techfest website.
        \end{list}

        \textbf{\href{https://play.google.com/store/apps/details?id=com.sports.cricket_now}{Cricket Now}}           \\%
        \emph{Flutter, Dart}
        \begin{list}{$\circ$}{}
            \item Android mobile app to watch live cricket scores, match history, ranking.
        \end{list}
    \end{multicols}

    %__________________________________________________________________________________________________________________
    % Skills
    \section{\mysidestyle Skills}

    \textbf{Frontend:} React, Backbone, Tailwind, SASS, Next.JS                                                     \\%
    \textbf{Backend:} Rails, Python, Node/Express                                                                   \\%
    \textbf{Mobile:} Flutter, React Native, Android App Development                                                 \\%
    \textbf{DevOps/Infra:} Kubernetes, CI/CD, (micro-)service oriented architecture                                 \\%
    \textbf{Tool/Services:} Git, GitHub, AWS, GCP, Docker                                                             %
\end{resume}
\end{document}
